\Russell's Metatheoretic Study - Abstract

### 2006-06-02 papers/ICFP'06-wmm/abstract-only.tex
li'll fixes again

\title{\Russell's Metatheoretic Study - Abstract}
\date{\today}
\author{Matthieu Sozeau \\
  LRI - Paris Sud - XI University \\
  \url{sozeau@lri.fr} -- \url{http://www.lri.fr/~sozeau}}
\begin{document}
\maketitle

@@

We will present these difficulties and our recipes for solving them in
the \Coq environment. Additionally, we will identify more general problems for
proving in \Coq and suggest possible solutions.

>>>>

\title{\Russell's Metatheoretic Study - Abstract}
\date{\today}
\author{Matthieu Sozeau \\
  LRI -- Paris Sud XI University \\
  \url{sozeau@lri.fr} -- \url{http://www.lri.fr/~sozeau}}
\begin{document}
\maketitle

@@

We will present these difficulties and our recipes for solving them in
the \Coq environment. Additionally, we will identify more general
problems arising in \Coq proofs and suggest possible solutions.
